\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation. The velocity magnitute is builded up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant. An slightly modified test-case follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
\subfigure[flow at t=250]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from (b) to (c) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{center}
\end{figure}

@@

@@

Having already verified that model is working for the test-cases illustrated in previous section, its to introduce a more complicated case where we have regions of different geometrical domains and different permeabilities. The time, the domain that we will use is defined in fig.\ref{fig:testcase_heter_domain}.

\begin{figure}[h]
\begin{center}

\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{a}}

\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase_heter_domain}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
}%
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}\\
\subfigure[MR1 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}
}%
\subfigure[MR10 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}\\
\subfigure[MR1 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}
}\\
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}
}\\
\end{center}
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
\label{fig:1testcase}
\end{figure}

>>>>

\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation. The velocity magnitute is builded up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant. An slightly modified test-case (see fig.\ref{fig:testcase}) follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$. The last set of simulations as this is described in fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
\subfigure[flow at t=250]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{c}}
\caption{In this test-case fixed and unstructured mesh is used. The aspect ratio is 2 (a), which allows the flow to develop for longer. Simulation time step increases from (b) to (c) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}%
}}%
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from (a) t=100(start) to (c) t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\KCnote{\blue{need to put screenshots from pseudo hele-shaw case - log on to Jeff's station and then include the following cases}}

Having already verified that model is working for the test-cases illustrated in previous section, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities. Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.

\begin{figure}[h]
\begin{center}
\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/map_of_boundaries.pdf}\label{a}}
\subfigure[permeabilities using an unstructured and fixed computational domain]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{b}}
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{center}
\end{figure}

@@
